### 2018-11-02 Writeup/PERT_New.tex
Change the data generation output
Finish the test_value

\bibliographystyle{plain}

@@

	\subsection{Test Cases Construction} \label{subsec:example}
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
	\subsection{Simulation Budget} \label{subsec:budget}
	\subsection{Computational Performance} \label{subsec:time}
\bibliographystyle{plain}
\bibliography{PERT_Bib}

>>>>

@@

	\subsection{Test Cases Construction} \label{subsec:example}
	\textcolor{blue}{Where we find our tests:
		\begin{itemize}
			\item Plambeck paper: Case 11
			\item V42: Case 14
			\item Case 19 from Elmgrabhy
			\item Case 55 from Elmgrabhy
			\item Randomized network 75, 100 nodes
			\item Plambeck paper: Case 110
	\end{itemize}}
	\noi Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem. Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value. We create one activity network with 14 activities and 
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption. First, we can solve a deterministic problem assuming no disruption occurs. Next, we can  three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
	\subsection{Simulation Budget} \label{subsec:budget}
	\subsection{Computational Performance} \label{subsec:time}
\bibliographystyle{plain}
\bibliography{PERT_Bib}
